Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-06-10 vesicle_code/docs/permeableVes/main.tex
pushing paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
We consider a semi-permeable vesicle in the poiseuille flow $\uu =
U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
initial reduced area is $\nu = 0.65$. In
Figure~\ref{fig:parabolicPhaseDiagram}, plot the steady state
configuration for a variety of flow rates $U$ and permeability rates
$\beta$. Similar to the shear example, we see that the flow rate has the
biggest effect on the final shape, and the effect of the permeability
rate is much weaker. Instead, the permeability rate determines the time
required for the vesicle to reach a steady state. In
Tables~\ref{tbl:parabolicRelaxTimes1}
and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
report the time, $t_\mathrm{steady}$, required for the vesicle's area to
be within 1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$,
required for the vesicle's area to exceed 1.3\% of its initial area. We
see that both times scale with $\beta^{-1}$.

@@

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Poiseuille Flow}
We consider a semi-permeable vesicle in the Poiseuille flow $\uu =
U(1-(y/R)^2,0)$, where $R=10$ determines the flow width, and $U$ is the
maximum flow rate. The length of the vesicle is $L = 4\pi$ and its
initial reduced area is $\nu = 0.65$. In
Figure~\ref{fig:parabolicPhaseDiagram}, plot the steady state
configuration for a variety of flow rates $U$ and permeability rates
$\beta$. Similar to the shear example, we see that the flow rate has the
biggest effect on the final shape, and the effect of the permeability
rate is much weaker. Instead, the permeability rate determines the time
required for the vesicle to reach a steady state. In
Tables~\ref{tbl:parabolicRelaxTimes1}
and~\ref{tbl:parabolicRelaxTimes2}, we consider two flow rates and
report the time, $t_\mathrm{steady}$, required for the vesicle's area to
be within 1.3\% of its maximum area, and the time, $t_\mathrm{inflate}$,
required for the vesicle's area to exceed 1.3\% of its initial area. We
see that both times scale with $\beta^{-1}$.

@@

Finally, we examine the effect of the non-linear Poiseuille flow in the
migration of semi-permeable vesicle. Similar to experiments performed by
Kaoui et al.~\cite{kao-bir-mis2009}, we initialize the vesicle's
center of mass above the $y$-axis and examine the y position of its
center of mass, denoted by $Y_G$.

\begin{itemize}
  \item If the flow rate is too small, the vesicle only migrates part
    way before it turns into a circle. Once it's a circle, it acts like
    a rigid body, so it no longer migrates towards the center line
\end{itemize}

@@

\input{figures/shearPhaseDiagramRA2.tikz}
